Evaluating FAIR Digital Object and Linked Data as distributed object systems

### 2023-06-17 latex/table1.tex
reference http rfcs

  & FDO types and operations enable detailed choreography (Canonical Workflow Frameworks for Research \autocite{cwfr}). \texttt{0.TYPE/DOIPOperation} has lightweight definition of operation, \texttt{0.DOIP/Request} or \texttt{0.DOIP/Response} may give FDO Type or any other kind of ``specifics'' (incl.~human readable docs). Semantics/purpose of operations not formalised (similar operations can be grouped with \texttt{0.DOIP/OperationReference}).
  & ``Follow your nose'' crawler navigation, which may lead to frequent dead ends. Operational composition, typically within a single API provider, documented by OpenAPI 3 \autocite{OpenAPISpecificationV3}, schema.org Actions \autocite{SchemaOrgActions}, WSDL/SOAP \autocite{w3-wsdl20-primer}, but frequently just as human-readable developer documentation/examples. \\

@@

  & \textcite{foundationDigitalObjectInterface} is transport-independent, commonly TLS TCP/IP port 9000), \href{https://www.cordra.org/documentation/api/doip-api-for-http-clients.html}{DOIP over HTTP}
  & HTTP/1.1 (TCP/IP port 80), HTTP/1.1+TLS (TCP/IP 443), HTTP/2 (as HTTP/1* but binary), HTTP/3 (like HTTP/2+TLS but UDP) \\

>>>>

  & FDO types and operations enable detailed choreography (Canonical Workflows; \textcite{cwfr}). \texttt{0.TYPE/DOIPOperation} has lightweight definition of operation, \texttt{0.DOIP/Request} or \texttt{0.DOIP/Response} may give FDO Type or any other kind of ``specifics'' (incl.~human readable docs). Semantics/purpose of operations not formalised (similar operations can be grouped with \texttt{0.DOIP/OperationReference}).
  & ``Follow your nose'' crawler navigation, which may lead to frequent dead ends. Operational composition, typically within a single API provider, documented by OpenAPI 3 \autocite{OpenAPISpecificationV3}, schema.org Actions \autocite{SchemaOrgActions}, WSDL/SOAP \autocite{w3-wsdl20-primer}, but frequently just as human-readable developer documentation with examples. \\

@@

  & \textcite{foundationDigitalObjectInterface} is transport-independent, commonly TLS TCP/IP port 9000, DOIP over HTTP \autocite{DOIPAPIHTTPa}
  & HTTP/1.1 TCP/IP port 80 \autocite{rfc2616}, HTTP/1.1+TLS TCP/IP 443 \autocite{rfc2818}, HTTP/2 (as HTTP/1* but binary) \autocite{rfc7540}, HTTP/3 (like HTTP/2+TLS but UDP) \autocite{rfc9114} \\
